Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2021-03-08 main.tex
:sparkles: Imperfect CSIT and quantized IRS

		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna User Equipment (UE) over $N$ orthogonal evenly-spaced subbands. We consider a quasi-static block fading model and focus on an instance where all channels are constant. The AP is assumed to have partial or perfect Channel State Information (CSI) of the AP-UE channel and the cascaded AP-IRS-UE channel. We also omit the signals reflected two and more times and assume the noise power is too small to be harvested.

@@

			At subband $n$, we denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and IRS-UE reflective channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$. The auxiliary link provided by the IRS can be modeled as a concatenation of the incident channel, the IRS reflection, and the reflective channel. Therefore, the composite equivalent channel reduces to
			\begin{equation}\label{eq:h_n}
				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{h}_{\mathrm{R},n}^H \boldsymbol{\Theta} \boldsymbol{H}_{\mathrm{I},n} = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
			\end{equation}
			where we define $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
		\end{subsection}

@@

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout in the simulation.}
			\label{fi:layout}
		\end{figure}
		To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize the average R-E regions under typical setups. Consider a large open space Wi-Fi-like environment at a center frequency of \SI{5.18}{\GHz} with bandwidth $B=1\,\si{\MHz}$ as reference. As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal path parallel to the AP-UE path and let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, respectively. We also denote $d_{\mathrm{D}}$, $d_{\mathrm{I}}$, $d_{\mathrm{R}}$ as the length of direct, incident, reflective paths such that $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$. $d_{\mathrm{D}}=15\,\si{\meter}$, $d_{\mathrm{V}}=2\,\si{\meter}$ and $d_{\mathrm{H}}=2\,\si{\meter}$ are chosen as reference. The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and the path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$. We assume all channels are NLoS with taps modelled as i.i.d. CSCG random variables of unit average sum-power, corresponding to a normalized multipath response. The reference numbers of transmit antennas, IRS elements and subbands are $M=1$, $L=20$, $N=16$, respectively. No spatial correlation is assumed across transmit antennas and IRS elements. Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=50\,\si{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$. The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ and the average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands as reference. We also assume a \SI{2}{\dBi} IRS element gain\footnote{Due to highly directional reflection.} and a \SI{2}{\dBi} receive antenna gain. For the algorithm, the tolerance is set to $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is set to $Q=10^{3}$, and the R-E region is averaged over \num{300} channel realizations. In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current. On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with the Water-Filling (WF) algorithm that allocates all power to the modulated waveform only. For a fair comparison, the $x$-axis of the plots has been normalized to the average subband rate $R/N$.

>>>>

		As shown in Fig.~\ref{fi:system}, we propose an IRS-aided SWIPT system where a $M$-antenna AP delivers information and power simultaneously, through a $L$-element IRS, to a single-antenna User Equipment (UE) over $N$ orthogonal evenly-spaced subbands. We assume perfect or partial Channel State Information at the Transmitter (CSIT) regarding the quasi-static AP-UE and AP-IRS-UE cascaded channels. The signals reflected two or more times are omitted and the noise power is assumed too small to be harvested.

@@

			At subband $n$, we denote the AP-UE direct channel as $\boldsymbol{h}_{\mathrm{D},n}^H \in \mathbb{C}^{1 \times M}$, AP-IRS incident channel as $\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$, and IRS-UE reflective channel as $\boldsymbol{h}_{\mathrm{R},n}^H \in \mathbb{C}^{1 \times L}$. The auxiliary link provided by the IRS can be modeled as a concatenation of the incident channel, the IRS reflection, and the reflective channel. Therefore, the composite equivalent channel reduces to
			\begin{equation}\label{eq:h_n}
				\boldsymbol{h}_{n}^H = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{h}_{\mathrm{R},n}^H \boldsymbol{\Theta} \boldsymbol{H}_{\mathrm{I},n} = \boldsymbol{h}_{\mathrm{D},n}^H + \boldsymbol{\phi}^H \boldsymbol{V}_{n}
			\end{equation}
			where we define the cascaded AP-IRS-UE channel without reflection as $\boldsymbol{V}_{n} \triangleq \mathrm{diag}(\boldsymbol{h}_{\mathrm{R},n}^H)\boldsymbol{H}_{\mathrm{I},n} \in \mathbb{C}^{L \times M}$.
		\end{subsection}

@@

	\begin{section}{Performance Evaluations}\label{se:performance_evaluation}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.9\columnwidth}
			\import{assets/}{layout.pdf_tex}
			\caption{System layout in the simulation.}
			\label{fi:layout}
		\end{figure}
		To evaluate the performance of the proposed IRS-aided SWIPT system, we characterize the average R-E regions under typical setups. Consider a large open space Wi-Fi-like environment at a center frequency of \SI{5.18}{\GHz} with bandwidth $B=1\,\si{\MHz}$ as reference. As shown in Fig.~\ref{fi:layout}, we assume the IRS moves along a horizontal path parallel to the AP-UE path and let $d_{\mathrm{H}}$, $d_{\mathrm{V}}$ be the horizontal and vertical distances from the AP to the IRS, respectively. We also denote $d_{\mathrm{D}}$, $d_{\mathrm{I}}$, $d_{\mathrm{R}}$ as the length of direct, incident, reflective paths such that $d_{\mathrm{I}}=\sqrt{d_{\mathrm{H}}^2+d_{\mathrm{V}}^2}$, $d_{\mathrm{R}}=\sqrt{(d_{\mathrm{D}}-d_{\mathrm{H}})^2+d_{\mathrm{V}}^2}$. $d_{\mathrm{D}}=15\,\si{\meter}$, $d_{\mathrm{V}}=2\,\si{\meter}$ and $d_{\mathrm{H}}=2\,\si{\meter}$ are chosen as reference. The path loss and fading parameters are obtained from IEEE TGn channel model D \cite{Erceg2004}, and the path loss is set to $L_0=-35\,\si{\dB}$ at $d_0=1\,\si{\meter}$. We assume all channels are NLoS with taps modelled as i.i.d. CSCG random variables of unit average sum-power, corresponding to a normalized multipath response. The reference numbers of transmit antennas, IRS elements and subbands are $M=1$, $L=20$, $N=16$, respectively. No spatial correlation is assumed across transmit antennas and IRS elements. Rectenna parameters are taken as $k_2=0.0034$, $k_4=0.3829$, $R_{\mathrm{A}}=50\,\si{\ohm}$ such that $\beta_2=0.17$ and $\beta_4=957.25$. The average Effective Isotropic Radiated Power (EIRP) is fixed to $P=36\,\si{\dBm}$ and the average noise power is $\sigma_n=-40\,\si{\dBm}$ at all subbands as reference. We also assume a \SI{2}{\dBi} IRS element gain\footnote{Due to highly directional reflection.} and a \SI{2}{\dBi} receive antenna gain. For the algorithm, the tolerance is set to $\epsilon=10^{-8}$, the number of candidates in the Gaussian randomization method is set to $Q=10^{3}$, and the R-E region is averaged over \num{300} channel realizations. In the R-E boundary, the leftmost point corresponds to WPT ($\rho=1$) where power can be allocated simultaneously to modulated and unmodulated waveform to maximize the average output DC current. On the other hand, the rightmost point corresponds to WIT ($\rho=0$) where the solution coincides with the Water-Filling (WF) algorithm that allocates all power to the modulated waveform only. For a fair comparison, the $x$-axis of the plots has been normalized to the average subband rate $R/N$. We also investigate the impact of imperfect CSIT and quantized IRS on the system performance.

		\begin{subsection}{Imperfect CSIT}
			Due to the general lack of RF-chains at the IRS, accurate CSIT acquisition can be challenging especially when the coherence time is short. Hence, we consider an imperfect CSIT model and denote the estimation of direct and cascaded links at subband $n$ as
			\begin{align}
				\hat{\boldsymbol{h}}_{\mathrm{D},n} &= \boldsymbol{h}_{\mathrm{D},n} + \tilde{\boldsymbol{h}}_{\mathrm{D},n} \\
				\hat{\boldsymbol{V}}_{n} &= \boldsymbol{V}_{n} + \tilde{\boldsymbol{V}}_{n}
			\end{align}
			where $\tilde{\boldsymbol{h}}_{\mathrm{D},n}$ and $\tilde{\boldsymbol{V}}_{n}$ are the corresponding estimation errors, whose entries follow i.i.d. CSCG distribution $\mathcal{CN}(0, \epsilon_{\mathrm{D},n}^2)$ and $\mathcal{CN}(0, \epsilon_{n}^2)$, respectively. Perfect CSIT can be regarded as a special case with $\epsilon_{\mathrm{D},n} = \epsilon_{n} = 0$. % For each direct and cascaded channel, we provide \num{100} channel estimates and examine the average R-E behavior.
		\end{subsection}

		\begin{subsection}{Quantized IRS}
			Recall in Remark \ref{re:reflection_coefficient} that one needs to vary the element impedance to adjust the reflection coefficient. To reduce the circuit complexity and control overhead, we design a passive beamforming codebook $\mathcal{C}_\phi = \{e^{j 2 \pi i / 2^b} \mid i = 1, \dots, 2^b\}$ and quantize each reflection coefficient by $b$ bits.
		\end{subsection}
